---
title: "Análises do Sivep-Gripe"
author: "Ana Carolina Moreno"
date: "27/04/2021"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Análises: Covid-19 no Estado de São Paulo
### Dados atualizados até **19/04/2021**

<!-- badges: start -->
<!-- badges: end -->

Essa página contém análises de dados de casos confirmados de Covid-19 no Estado de São Paulo.


```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

You can also embed plots, for example:

```{r pressure, echo= FALSE}

plot(pressure)

```

Teste da Carol

```{r ggplot_covid_sp_dia, echo=F}

library(tidyverse)
library(lubridate)
library(zoo)
library(readr)
library(ggplot2)
library(tidylog)
library(ggthemes)
library(lme4)

ggplot_covid_sp_dia <- read_rds("data/covid_sp_dia.rds") %>%
  ggplot(aes(x=data, y=valor, group=categoria, colour=categoria)) +
  geom_line()+
  labs(y = 'Total de internações por dia',
       x = 'Fonte: Censo Covid/SES-SP')+
  ggtitle("Novas internações e novas mortes confirmadas por Covid-19 (Estado de SP)")+
  theme(
    plot.background = element_rect(fill = "white"),
    panel.background = element_rect(fill = "white", colour="grey"),
    panel.grid.major = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.minor = element_line(colour = "grey", linetype = "dotted"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
  )+
  geom_vline(xintercept=ymd("2021-03-24"), color="blue", size=0.2)
```

Teste 2

```{r ggplot_covid_sp_dia}


plot(ggplot_covid_sp_dia)
```




In that case, don't forget to commit and push the resulting figure files, so they display on GitHub.
